---
title: "Binomial Function Starter Kit"
author: "Shivansh Kumar"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Binomial Package}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(binomial)
```

## Binomial Distribution Package Starter Kit

The **binomial** package implements different functions and methods that calculate and display different summary measures of different binomial objects. There are also functions that can be used to create a binomial object that can be used to find the probability of success based on different parameter values that describe this binomial function.

## Getting Started with Binomial Package

Load the binomial package and other required packages into the workspace with the code below:
```{r}
library(binomial)
library(ggplot2)
```

In the binomial package, there are some *main functions* that can be used to describe different binomial distributions with examples on how to use.

1. **bin_choose**:  Binomial choose function that computes the number of combinations in which `k` successes can occur in `n` trials.
```{r bin_choose}
bin_choose(n = 10, k = 5)
```

2. **bin_probability**:  Binomial probability function that computes the probability of getting `k` successes in `n` trials with probability of success `prob`.
```{r bin_probability}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

3. **bin_distribution**: Binomial distribution function that creates a binomial distribution data frame using the binomial probability function with successes and probabilities as columns.
```{r bin_distribution}
bin_distribution(trials = 5, prob = 0.5)
```

Method used with `bin_distribution` function that graphs barplot to display probability histogram of binomial distribution object "bindis":
```{r plot_bin_distribution}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

4. **bin_cumulative**: Binomial cumulative function that creates a binomial distribution data frame using the binomial probability function with successes, probabilities, and cumulative probabilities as columns.
```{r bin_cumulative}
bin_cumulative(trials = 5, prob = 0.5)
```

Method used with `bin_cumulative` function that graphs the cumulative distribution of binomial distribution object "bincum":
```{r plot_bin_cumulative}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```

5. **bin_variable**: Binomial random variable function that returns an object of class "binvar" that is a binomial random variable object.
```{r bin_variable}
bin_variable(trials = 5, prob = 0.5)
```

Method used with `bin_variable` function that graphs the cumulative distribution of binomial distribution object "bincum":
```{r print_bin_variable}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
```

Method used with `bin_variable` function that gives the full summary description of an object "binvar":
```{r summary_bin_variable}
bin1 <- bin_variable(trials = 10, p = 0.3)
summary(bin1)
```

Method used with `bin_variable` function and summary method that prints the summary.binvar object:
```{r print_bin_variable_sum}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```

** Summary Measures Descriptions **

1. *Mean* = $np$

2. *Variance* = $np(1 - p)$

3. *Mode* = $int(np + p)$

4. *Skewness* = $\frac{1 - 2p}{\sqrt{np(1 - p)}}$

5. *Kurtosis* = $\frac{1 - 6p(1 - p)}{np(1 - p)}$

Can also directly calculate these summary measures using functions below:
```{r summary_measures}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```

## Extra Help
If need more documentation, can call the help function on any of the functions described above in this vignette.

Example for calling help function on bin_choose:
```{r eval = FALSE}
help(bin_choose)
```
